---
title: "Management and Organizational Practices Survey - Colombia 2017-2018"
author: "Leonardo Iacovone / Javier Fernandez"
date: "7/21/2020"
output:
  pdf_document: default
  word_document: default
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r echo=FALSE,warning=(FALSE),message=FALSE}


#install.packages("stargazer")
#install.packages("tidyverse")
#install.packages("ggplot2")
#install.packages("dplyr")
#install.packages("kableExtra")
#install.packages("xtable")
#install.packages("knitr")
#install.packages("papeR")
#install.packages("devtools")
#install.packages("tinytex")
#tinytex::install_tinytex()
#tinytex:::install_prebuilt()
#tinytex::install_tinytex()
#devtools::install_github('yihui/tinytex')
#tinytex::reinstall_tinytex()
library(tinytex)
#update.packages(ask = FALSE, checkBuilt = TRUE)
#tinytex::tlmgr_update()
options(tinytex.verbose = TRUE)
#install.packages("booktabs")
#install.packages("miceadds")


library(tidyverse)
library(ggplot2)
library(stargazer)
library(dplyr)
library(kableExtra)
library(xtable)
library("knitr")
library("papeR")
library("devtools")
require(plyr)
#install.packages("IDPmisc")
library(IDPmisc)
library(lmtest)
library(estimatr)
library(plm)
library(fastDummies)
library(texreg)
library(fixest)
library(miceadds)


library(haven)
Edit_2017_2018_1 <- read_dta("~/Google Drive/Internship_WB_Summer/Edit/Github/My_internship/Edit 2017_2018_recoded.dta")


####Cleaning for managers-frequency review. If No key performance indicators (from question 2), question 3 will be zero
#(if VIII5R1C1_new=0 (Dane:VIII5R1C1=5), VIII6R1C1_new,VIII7R1C1_new, VIII8R1C1_new should be = 0)

Edit_2017_2018_1 <- Edit_2017_2018_1 %>%
  mutate(VIII6R1C1_new = ifelse(VIII5R1C1_new== 0, 0, VIII6R1C1_new))
Edit_2017_2018_1 <- Edit_2017_2018_1 %>%
  mutate(VIII6R2C1_new = ifelse(VIII5R1C1_new== 0, 0, VIII6R2C1_new))
Edit_2017_2018_1 <- Edit_2017_2018_1 %>%
  mutate(VIII6R3C1_new = ifelse(VIII5R1C1_new== 0, 0, VIII6R3C1_new))
Edit_2017_2018_1 <- Edit_2017_2018_1 %>%
  mutate(VIII6R4C1_new = ifelse(VIII5R1C1_new== 0, 0, VIII6R4C1_new))
Edit_2017_2018_1 <- Edit_2017_2018_1 %>%
  mutate(VIII6R5C1_new = ifelse(VIII5R1C1_new== 0, 0, VIII6R5C1_new))
Edit_2017_2018_1 <- Edit_2017_2018_1 %>%
  mutate(VIII6R6C1_new = ifelse(VIII5R1C1_new== 0, 0, VIII6R6C1_new))
Edit_2017_2018_1 <- Edit_2017_2018_1 %>%
  mutate(VIII6R7C1_new = ifelse(VIII5R1C1_new== 0, 0, VIII6R7C1_new))

#Cleaning for no-managers-frequency-review. If No key performance indicators (from question 2), question 4 will be zero 
Edit_2017_2018_1 <- Edit_2017_2018_1 %>%
  mutate(VIII7R1C1_new = ifelse(VIII5R1C1_new== 0, 0, VIII7R1C1_new))
Edit_2017_2018_1 <- Edit_2017_2018_1 %>%
  mutate(VIII7R2C1_new = ifelse(VIII5R1C1_new== 0, 0, VIII7R2C1_new))
Edit_2017_2018_1 <- Edit_2017_2018_1 %>%
  mutate(VIII7R3C1_new = ifelse(VIII5R1C1_new== 0, 0, VIII7R3C1_new))
Edit_2017_2018_1 <- Edit_2017_2018_1 %>%
  mutate(VIII7R4C1_new = ifelse(VIII5R1C1_new== 0, 0, VIII7R4C1_new))
Edit_2017_2018_1 <- Edit_2017_2018_1 %>%
  mutate(VIII7R5C1_new = ifelse(VIII5R1C1_new== 0, 0, VIII7R5C1_new))
Edit_2017_2018_1 <- Edit_2017_2018_1 %>%
  mutate(VIII7R6C1_new = ifelse(VIII5R1C1_new== 0, 0, VIII7R6C1_new))
Edit_2017_2018_1 <- Edit_2017_2018_1 %>%
  mutate(VIII7R7C1_new = ifelse(VIII5R1C1_new== 0, 0, VIII7R7C1_new))


#### AVERAGE score for managers-frequency review, question 3

Edit_2017_2018_1$VIII6_new_avg_score = rowMeans(Edit_2017_2018_1[,c(680,681,682,683,684,685,686)],na.rm = TRUE)

#### AVERAGE score for no Managers-frequency review, question 4

Edit_2017_2018_1$VIII7_new_avg_score = rowMeans(Edit_2017_2018_1[,c(687,688,689,690,691,692,693)],na.rm = TRUE)


#### AVERAGE score for non-managers’ performance bonuses based on, question 9
Edit_2017_2018_1$VIII12_new_avg_score = rowMeans(Edit_2017_2018_1[,c(700,701,702,703,704)],na.rm = TRUE)

#### AVERAGE score for managers’ performance bonuses usually based on, question 11
Edit_2017_2018_1$VIII14_new_avg_score = rowMeans(Edit_2017_2018_1[,c(706,707,708,709,710)],na.rm = TRUE)


Edit_2017_2018_1$VIII10R1C1_new <- replace(Edit_2017_2018_1$VIII10R1C1_new, Edit_2017_2018_1$VIII10R1C1_new == 6, NA)

#VIII19R1C1, question property
Edit_2017_2018_1$property<-as.character(Edit_2017_2018_1$VIII1R1C1)
Edit_2017_2018_1$property<-revalue(Edit_2017_2018_1$property,c("1"="Founder","2"="Founder's Familiy","3"="Other"))
#Edit_2017_2018_1$property<-as.numeric(Edit_2017_2018_1$property)

#this lines to identify number of column and variable
#data.frame(colnames(Edit_2017_2018_1))

#variable:column number:question number (1-16 - Bloom (2019))
# VIII4R1C1_new=678=q1, VIII5R1C1_new=679=q2,VIII6_new_avg_score=694=q3,VIII7_new_avg_score=695=q4,VIII8R1C1_new=696=q5
#VIII9R1C1_new=697=q6,VIII10R1C1_new=698=q7,VIII11R1C1_new=699=q8,VIII12_new_avg_score=716=q9,VIII13R1C1_new=705=q10
# VIII14_new_avg_score=717=q11,VIII15R1C1_new=711=q12,VIII16R1C1_new=712=q13,VIII17R1C1_new=713=q14,
#VIII18R1C1_new=714=q15,VIII19R1C1_new=715=q16

# counting missing values accross 16 questions
Edit_2017_2018_1$na_16_q<-rowSums(is.na(Edit_2017_2018_1[, c(678,679,694,695,696,697,698,699,716,705,717,711,712,713,714,715)]))

#filtering the data set: From 16 Bloom Questions,at least 11 non-missing values (max 5 missing values)
Edit_2017_2018_2 <- Edit_2017_2018_1[Edit_2017_2018_1$na_16_q <=5,]



```


```{r results="asis",echo=FALSE,warning=(FALSE),message=FALSE}

#Management Score, Non-incentives and incentives questions

# 1. Total Average (16 questions)
Edit_2017_2018_2$Management = rowMeans(Edit_2017_2018_2[,c(678,679,694,695,696,697,698,699,716,705,717,711,712,713,714,715)],na.rm = TRUE)

# 2.Non-incentives average (1-8 questions)

Edit_2017_2018_2$avg_non_inc_q = rowMeans(Edit_2017_2018_2[,c(678,679,694,695,696,697,698,699)],na.rm = TRUE)

# 3.Incentives average (9-16 questions)

Edit_2017_2018_2$avg_inc_q = rowMeans(Edit_2017_2018_2[,c(716,705,717,711,712,713,714,715)],na.rm = TRUE)

```


```{r echo=FALSE,warning=(FALSE),message=FALSE,results="asis"}

#Descriptive Statistics

library(haven)
#reading Annual Manufacturing Survey from Colombia
Eam_2018_1 <- read_dta("~/Google Drive/Internship_WB_Summer/Edit/Github/My_internship/EAM_2018_30june.dta")

###proportion of multiplants
count_nordemp_eam<-data.frame(count(Eam_2018_1,"nordemp"))

count_nordemp_eam<-count_nordemp_eam %>%
   mutate(Multiplant = if_else(freq >1, 1,0))

### exporters###

Edit_2017_2018_2<-Edit_2017_2018_2 %>%
   mutate(Exporters = if_else(I3R2C2 >1, 1,0))

####reshape

#require(reshape2)
#mat$id <- rownames(mat) 
#melt(mat)

##dataframe for stargazer
df0<-data.frame(Edit_2017_2018_2$NORDEMP,Edit_2017_2018_2$Management,Edit_2017_2018_2$avg_non_inc_q,Edit_2017_2018_2$avg_inc_q,Edit_2017_2018_2$IV1R11C2,Edit_2017_2018_2$Exporters)

colnames(df0)[1] <- "nordemp"
colnames(df0)[2] <- "Management (1-16)"
colnames(df0)[3] <- "No Incentives (1-8)"
colnames(df0)[4] <- "Incentives (9-16)"
colnames(df0)[5]<-"Size(Firm employment)"
colnames(df0)[6]<-"Exporters"

df0 <- merge(df0,count_nordemp_eam,by="nordemp",all=FALSE)

#selection fixed effect variables (dpto,ciiu4)
dffe1<-subset(Eam_2018_1,select=c(nordemp,dpto,ciiu4))
#picks the first in each block of repetitions of establishments
dffe2<-dffe1[ !duplicated(dffe1$nordemp), ]
colnames(dffe2)[1] <- "NORDEMP"

dft=subset(df0, select = -c(nordemp,freq))

stargazer(dft,
          header = FALSE,
          title = "Descriptive Statistics (1)",
          digits = 3,
          df = FALSE,
          notes.append=TRUE,
          notes.align = "l",
          notes = c("Note:The management score is the unweighted average of the score for each of the 16 questions, where",                              "each question is first normalized to be on a 0-1 scale. The sample in all columns is allobservations",
                   "with at least 11 non-missing responses to management questions and a successful match to EAM.")) 


#install.packages("texreg")


```


The next histogram shows the distribution for magement score (16 questions). As you can see, the distribution is skewed to the left, where the total number of observations is 7,529 in EDIT. This histogram includes all observations with at least 11 non-missing responses to management questions.



```{r echo=FALSE,warning=(FALSE),message=FALSE, fig.show='hide',results='hide'}

# Histogram Colombia - USA with only EDIT data

my.hist1<-hist(Edit_2017_2018_2$Management, ylab ="Probability", breaks=20)

my.hist1$counts
mycount1<-data.frame(my.hist1$counts)

score_bar<-data.frame(c("0.05","0.1","0.15","0.2","0.25","0.3","0.35","0.4","0.45","0.5","0.55","0.6","0.65","0.7","0.75","0.8","0.85","0.9","0.95","1"))
colnames(score_bar)[1]<-"Score"
usa_freq <-data.frame(c("0.0011","0.0016","0.0041","0.0131","0.0191","0.0251","0.0311","0.0451","0.0581", "0.0641", "0.0883", "0.0961", "0.1201","0.1161","0.1131","0.0951","0.0561","0.0221","0.0281","0.0024"))
colnames(usa_freq)[1] <- "USA"
col_freq1 <- prop.table(mycount1)
colnames(col_freq1)[1] <- "Colombia"


#df <- data.frame(, second_column)
my_over_hist1<-data.frame(score_bar,usa_freq,col_freq1)

my_over_hist1$Score<-as.numeric(as.character(unlist(my_over_hist1[[1]])))
my_over_hist1$USA<-as.numeric(as.character(unlist(my_over_hist1[[2]])))
my_over_hist1$Colombia<-as.numeric(as.character(unlist(my_over_hist1[[3]])))
#typeof(my_over_hist$Colombia)

```

```{r echo=FALSE,warning=(FALSE),message=FALSE}

# Plot comparing USA and Colombia Scores

library(ggplot2)

ggplot(data=my_over_hist1,aes(x=Score))+
  geom_bar(aes(y=Colombia),stat="identity",position ="identity",alpha=.5,fill='black',color='red') +
  geom_bar(aes(y=USA),stat="identity",position ="identity",alpha=.5,fill='white',color='blue')+ 
  labs(title = "Manegement - Colombia vs USA with only EDIT data",
       x="Score: Colombia(red) - USA(blue)",
       y="Share")+theme(plot.title = element_text(hjust = 0.5))+theme(plot.title = element_text(hjust = 0.5))

```


According to Bloom(2019) the average U.S Management score (1-16 questions) is 0.615, the non-incentives (1-8) is 0.643 and the incentives (9-16) is 0.583.


The next table shows the number of observations for each database and our estimates use the merge EDIT-EAM. 

```{r echo=FALSE,warning=(FALSE),message=FALSE,results="asis"}

# observations

#aggregating by nordemp and summing dpto or more.
# As a result, the new variable is Group.1 (KEY) instead nordemp (Nominal change) and the aggregated variable is x instead dpto.
Eam_2018_2<-aggregate(list(Eam_2018_1$CONSIN2, Eam_2018_1$ACTIVFI,Eam_2018_1$PERTOTAL,Eam_2018_1$PRODBR2,Eam_2018_1$c7c4r14,Eam_2018_1$VALAGRI,Eam_2018_1$PRESPYTE,Eam_2018_1$SALPEYTE,Eam_2018_1$VALORVEN,Eam_2018_1$VALORCOM,Eam_2018_1$VALORCX,Eam_2018_1$PORCVT), by=list(Eam_2018_1$nordemp),FUN=sum,na.rm=TRUE) #, na.rm=FALSE

#ascendent order on Group.1, it is optional becaise the aggregate function returns a ascendent Group.1 (KEY) 
#Eam_2018_3<- Eam_2018_2[order(Eam_2018_2$x),]
#testing a specific value on a variable
#any(Eam_2018_3$Group.1==141465)

# returns the variable names easily
#data.frame(colnames(Eam_2018_2))

#changing names
colnames(Eam_2018_2)[1] <- "NORDEMP"
colnames(Eam_2018_2)[2] <- "intinput"
colnames(Eam_2018_2)[3] <- "fixedassets"
colnames(Eam_2018_2)[4] <- "empltot"
colnames(Eam_2018_2)[5] <- "valprod"
colnames(Eam_2018_2)[6] <- "valitc"
colnames(Eam_2018_2)[7]<-"valueadded"
colnames(Eam_2018_2)[8]<-"benefits"
colnames(Eam_2018_2)[9]<-"wages"
colnames(Eam_2018_2)[10]<-"sales"
colnames(Eam_2018_2)[11]<-"raw_material"
colnames(Eam_2018_2)[12]<-"raw_material_m"
colnames(Eam_2018_2)[13]<-"sales_x"


#typeof(Eam_2018_2$dpto)
#typeof(Eam_2018_2$periodo)
#summarise(Eam_2018_2)

#Natural join (all=FALSE, only intersection)
total <- merge(Edit_2017_2018_2,Eam_2018_2,by="NORDEMP",all=FALSE)
#Natural join with ciiu4 and dto
total<-merge(total,dffe2,by="NORDEMP",all=FALSE)


n<-data.frame(Database=c("EDIT 1:All observations","EDIT 2:At least 11 non-missing values","EAM 1:All observations","EAM 2:Collapsed data","Merge EDIT 2 - EAM 2"),n=c(nrow(Edit_2017_2018_1),nrow(Edit_2017_2018_2),nrow(Eam_2018_1),nrow(Eam_2018_2),nrow(total)))
#kable(n)%>%
#  kable_styling(position = "center")

stargazer(n,
          header = FALSE,
          title = "Databases",
          digits = 3,
          df = FALSE,
          summary=FALSE,
          rownames = FALSE)

# Total sales from EDIT
total$salesEdit<-total$I3R2C1+total$I3R2C1

#dataframe for Stargazer 
dft2=subset(total, select = c(NORDEMP,sales,valueadded,salesEdit,sales_x,II1R10C2))#sharesales_x,sharesRDi
#Cleaning
dft2<-dft2[!(dft2$sales=="0"|dft2$salesEdit=="0"),]

#javis<-data.frame(count(dft2,"sharesRDi"))

dft2<-dft2%>%
  mutate(sales=sales/1000)%>%
  mutate(sales_x=sales_x/1000)%>%
  mutate(valueadded=valueadded/1000)%>%
  mutate(sharesales_x=sales_x/sales)%>%
  mutate(sharesRD=II1R10C2/salesEdit)

dft2=subset(dft2, select = -c(salesEdit,sales_x,II1R10C2))

#outliers: NORDEMP=981456,144974,145804,145918 because they have outliers on RDi>0.9
dft2<-dft2[!(dft2$NORDEMP=="981456"|dft2$NORDEMP=="144974"|dft2$NORDEMP=="145804"|dft2$NORDEMP=="145918"),]
dft2=subset(dft2, select = -c(NORDEMP))

#CLEANING outliers
total<-total[!(total$NORDEMP=="981456"|total$NORDEMP=="144974"|total$NORDEMP=="145804"|total$NORDEMP=="145918"),]

colnames(dft2)[1] <- "Total Sales"
colnames(dft2)[2] <- "Value Added"
colnames(dft2)[3] <- "Exports/Sales"
colnames(dft2)[4] <- "RDi/Sales"


stargazer(dft2,
          header = FALSE,
          title = "Descriptive Statistics (2)",
          df = FALSE,
          notes.append=TRUE,
          notes.align = "l",
          notes = c("Note:For the merge between EDIT and EAM,this table shows the descriptive statistics for Total Sales",
                    "Value Added in millions of colombian pesos, value of exported products/Sales and value of investment",
                    "on research, development and innovation (RDi)/Sales.")) 


```



```{r echo=FALSE,warning=(FALSE),message=FALSE,results="asis", fig.show='hide',results='hide'}


my.hist2<-hist(total$Management, ylab ="Probability", breaks=20)

my.hist2$counts
mycount2<-data.frame(my.hist2$counts)
col_freq2 <- prop.table(mycount2)
colnames(col_freq2)[1] <- "Colombia"

#df <- data.frame(, second_column)
my_over_hist2<-data.frame(score_bar,usa_freq,col_freq2)

my_over_hist2$Score<-as.numeric(as.character(unlist(my_over_hist2[[1]])))
my_over_hist2$USA<-as.numeric(as.character(unlist(my_over_hist2[[2]])))
my_over_hist2$Colombia<-as.numeric(as.character(unlist(my_over_hist2[[3]])))


```
The next histogram shows the distribution for magement score (16 questions) for Colombia and the United States, using the merge between EDIT and EAM with 6,034 observations. 

```{r echo=FALSE,warning=(FALSE),message=FALSE,results="asis"}

# Histogram Colombia - USA with merge between EDIT - EAM 

library(ggplot2)

ggplot(data=my_over_hist2,aes(x=Score))+
  geom_bar(aes(y=Colombia),stat="identity",position ="identity",alpha=.5,fill='black',color='red') +
  geom_bar(aes(y=USA),stat="identity",position ="identity",alpha=.5,fill='white',color='blue')+ 
  labs(title = "Manegement - Colombia vs USA with merge EDIT - EAM data",
       x="Score: Colombia(red) - USA(blue)",
       y="Share")+theme(plot.title = element_text(hjust = 0.5))
```


```{r echo=FALSE,warning=(FALSE),message=FALSE,results="asis"}

#### Mangement and Employment###
#tranformation of employment= A company should have at least 1 employment. Just 3 cases are adjusted, from 0 to 1
total<-total%>%
  mutate(empltot2=ifelse(empltot==0,1,total$empltot))
total$logempltot2<-log(total$empltot2)

#creating the log employment adjusted
total$logempltot2<-log(total$empltot2)


##### ggplot#####

p <- ggplot(data = total,                # specify dataset
            aes(x = Management, y = logempltot2))+labs(x="Management",y="Log Employment", title="Firm size rises with Management -Non-Linear fit") + # Age on x-, Raven on y-axis
  geom_point(pch = 1,size=0.05)+theme(plot.title = element_text(hjust = 0.5))

q1 <- p +
  geom_smooth() # add scatterplot smoother
q1

```

```{r echo=FALSE,warning=(FALSE),message=FALSE,results="asis"}

#install.packages("StatMeasures")
library(StatMeasures)
#install.packages("scales")
library(scales)

##############BAR GRAPHS##################
#listing variables to plot (Productivity,Exports, RD and i,Profit,) and some? which?
#1. Productivity (value added/employees)
total$productivity<-total$valueadded/total$empltot2
total$productivity3<-(total$productivity)/1000
#2. Value of Exports: I3R2C2
total$exports_millions<-(total$I3R2C2)/1000
#3. Investement on RD and Innovation: II1R10C2
total$rdi_millions<-(total$II1R10C2)/1000
#4. Operating profit
#a. total wages
total$totalwages<-total$benefits+total$wages
#b. Total expenses
total$totalexpenses<-total$totalwages+total$intinput
#Operating profit
total$opprofit<-total$valprod-total$totalexpenses
total$opprofit_millions<-(total$opprofit)/1000
# 5. intellectual property registers
total$ipr<-total$VI1R8C2
# 6. Wage/Empl - 2018
total$wage_per_emp<-total$totalwages/total$empltot



#summary(total$valueadded)

#### Decile graphs######
total$decilmanagement<-ntile(total$Management,10)

bar1<-ggplot(total, aes(x=decilmanagement, y=productivity3))+labs(x="Decile of Management", y="Labor Productivity")+ stat_summary(fun = "mean",geom = "bar")

bar2<-ggplot(total, aes(x=decilmanagement, y=exports_millions))+ 
  labs(x="Decile of Management", y="Av. Exports") +stat_summary(fun = "mean", geom = "bar")

bar3<-ggplot(total, aes(x=decilmanagement, y=rdi_millions))+ 
  labs(x="Decile of Management", y=" Av. RDi") +stat_summary(fun = "mean", geom = "bar")
  
bar4<-ggplot(total, aes(x=decilmanagement, y=opprofit_millions))+ 
  labs(x="Decile of Management", y="Av. Operating Profit_Mill") +stat_summary(fun = "mean", geom = "bar")

bar5<-ggplot(total, aes(x=decilmanagement, y=ipr))+ 
  labs(x="Decile of Management", y="Av. IP registers") +stat_summary(fun = "mean", geom = "bar")

bar6<-ggplot(total, aes(x=decilmanagement, y=wage_per_emp))+ 
  labs(x="Decile of Management", y="Av.(Wage/Emp)") +stat_summary(fun = "mean", geom = "bar")


#install.packages("ggpubr")
library(ggpubr)
ggarrange(bar1, bar2, bar3 , bar4, bar5, bar6+rremove("x.text"),
          ncol = 2, nrow = 3)+theme(plot.title = element_text(hjust = 0.5))



```


Suppose that the firm production function is:

$$Y_{i} = A_{i}K_{i}^{\alpha}L_{i}^{\beta}I^{\gamma}e^{\delta M_{i}}e^{\mu X_{i}} + \varepsilon_{i}$$
Where $Y_{i}$:Production of firm i
$A_{i}$: Total factor productivity (Excluding Management Practices)
$K_{i}$:Fixed assets at final of 2018
$L_{i}$:Labor inputs: the total number of employees of firm i
$I_{i}$:Intermediate inputs
$X_{i}$:Vector of additional factors: the percent of staff with college degree
$M_{i}$: Management score (1-16)


Dividing by labor and taking logs we can rewrite this in a form to estimate on the
data:

$$log\frac{Y_{i}}{L_{i}} = \alpha log\frac{K_{i}}{L_{i}} + \gamma log \frac{I_{i}}{L_{i}} + (\alpha+ \beta  +\gamma)log L_{i} +\delta M_{i} + \mu X_{i} + u_{i} $$
We calculate this equation by estimating an OLS regression

```{r echo=FALSE,warning=(FALSE),message=FALSE,results="asis"}


#########################REGRESSIONS IN LOGARITHMS#############

#List of variables for Manegement score and performance FOR ALL REGRESSIONS
#With Logarithms 
#1. Percent of staff_with_college_degree=staff_with_college_degree
total$staff_with_college_degree<-total$IV1R4C2/total$IV1R11C2
#2. Log (production/employees)
total$lnprod<-log(total$valprod/total$empltot)
#2B. Log (sales/employees)
total$lnsales<-log(total$sales/total$empltot)
#3. Log (total employment)=lnempltot
total$lnempltot<-log(total$empltot)
#4. Total Score (1-16)=Management
#5. Log (fixed assets / employees)=lnfape
total$lnfape<-log(total$fixedassets/total$empltot)
#6.Log (intermediate inputs/employees): lniipe
total$lniipe<-log(total$intinput/total$empltot)
##7.Profits/sales=profoversales
total$sales_millions<-total$sales/1000
total$profoversales<-total$opprofit_millions/total$sales_millions
#8.Log (Profit/sales)
total$lnprofoversales<-log(total$profoversales)
#9.Lerner Index
total$lerner<-total$opprofit/total$sales
total$ciiu4_2_d<- substr(total$CIIU4, start = 1, stop = 2)
#10. Ln production
total$lnvalprod<-log(total$valprod)
#11. Ln wages
total$lnwages<-log(total$totalwages)
#12. Ln Fix assets
total$lnfixedassets<-log(total$fixedassets)
#13. Ln Intermediate input
total$lnintinput<-log(total$intinput)


#List of variables for Drivers of Productivity variation
#With logarithms 
#0. Log (Value Added/Employees)
total$log_Value_Added_per_Employee<-log(total$valueadded/total$empltot)
#1.Total Score (1-16): total$Management
#2. RDi/emp=II1R10C2/empltot
total$RDi<-total$II1R10C2
total$RDi_per_empl=(total$RDi/total$empltot)
total$RDi_per_empl1=(total$RDi_per_empl)+1
total$lnRDi_per_empl1=log(total$RDi_per_empl1) ####This the variable for RD
#3.Investment on ITC/Emp) - 2018:total$II1R4C2/total$empltot
total$ICT_per_Employee<-total$II1R4C2/total$empltot #### This the variable, since unit are miles, this means spending per 1000 workers


###########  Plant Management Scores and Performance (Bloom, 2019: Table 1)

#subset1


g1_1<-subset(total,select=c(NORDEMP,lnprod,lnsales,profoversales,Management,lnfape,lniipe,lnempltot,staff_with_college_degree,CIIU4,dpto))
g1_1<-NaRV.omit(g1_1)
g1_2<-subset(total,select=c(NORDEMP,lnsales,Management,lnfape,lniipe,lnempltot,staff_with_college_degree,CIIU4,dpto))
g1_2<-NaRV.omit(g1_2)
g1_3<-subset(total,select=c(NORDEMP,profoversales,Management,lnfape,lniipe,lnempltot,staff_with_college_degree,CIIU4,dpto))
g1_3<-NaRV.omit(g1_3)


m1 <- miceadds::lm.cluster(lnprod ~ Management+lnfape+lniipe+lnempltot+staff_with_college_degree+factor(CIIU4),cluster="CIIU4", data = g1_1)


m2 <- miceadds::lm.cluster(lnprod ~ Management+lnfape+lniipe+lnempltot+staff_with_college_degree+factor(dpto),cluster="dpto",data = g1_1)

m3<-lm(lnprod ~ Management+lnfape+lniipe+lnempltot+staff_with_college_degree,data=g1_1)

#Log(sales/employees)

m4 <- miceadds::lm.cluster( lnsales~ Management+lnfape+lniipe+lnempltot+staff_with_college_degree+factor(CIIU4),cluster="CIIU4",data = g1_2)

m5 <- miceadds::lm.cluster(lnsales ~ Management+lnfape+lniipe+lnempltot+staff_with_college_degree+factor(dpto),cluster="dpto",data = g1_2)

m6<-lm(lnsales ~ Management+lnfape+lniipe+lnempltot+staff_with_college_degree,data=g1_2)

#Log(profit/employees)

m7 <- miceadds::lm.cluster(profoversales~ Management+lnfape+lniipe+lnempltot+staff_with_college_degree+factor(CIIU4),cluster="CIIU4",
                      data = g1_3)

m8 <- miceadds::lm.cluster(profoversales ~ Management+lnfape+lniipe+lnempltot+staff_with_college_degree+factor(dpto),cluster="dpto",data = g1_3)

m9<-lm(profoversales ~ Management+lnfape+lniipe+lnempltot+staff_with_college_degree,data=g1_3)


#stargazer(m1,m2,m3,m4,m5,m6,m7,m8,m9,
#          header = FALSE,
#          title = "Firm Management Scores and Performance ",
#          covariate.labels = c("Management", "Ln(Cap/Emp)","Ln(Input/Emp)","Ln(Employment)","Degree"),
#          dep.var.labels = c("Ln(Output/Emp)","Ln(Sales/Emp)","Profit/Sales"),#,
#          model.names = FALSE,
#          omit.stat = c("ser","f","adj.rsq"), #"rsq", 
#          omit="Constant",
#          digits = 2,
#          notes.align = "l",
#          font.size = "footnotesize")



texreg(list(m1, m2,m3,m4,m5,m6,m7,m8,m9),caption.above = TRUE, caption="Firm Management Scores and Performance",fontsize = "small", custom.header = list("Ln(Output/Emp)"=1:3,"Ln(Sales/Emp)"=4:6, "Profit/Sales"=7:9),digits =2,omit.coef =c("(Intercept)|(factor)"),custom.coef.names=c("Management","Ln(Cap/Emp)", "Ln(Input/Emp)", "Ln(Employment)","Degree"), custom.model.names =c("1","2","3","4","5","6","7","8","9"),custom.note = ("\\parbox{0.95\\linewidth}{\\vspace{3pt}%stars. \\\\OLS coefficients with standard errors in parentheses. The management score is the unweighted average of the score for each of the 16 questions, where each question is first normalized to be on a 0–1 scale. The sample is all EDIT observations with at least 11 non-missing responses to management questions and a successful match to EAM, which have positive value added, positive employment, and positive imputed capital. The columns 1-3 mean the models with Industry Fixed Effects, Location Fixed Effects and no Fixed Effects, respectively.This also applies for columns 4-6 and 7-9}")) 



```



```{r echo=FALSE,warning=(FALSE),message=FALSE,results="asis"}


#subset2
g2_1<-subset(total,select=c(NORDEMP,log_Value_Added_per_Employee,Management,lnfape,lnempltot,staff_with_college_degree,CIIU4,dpto))
g2_1<-NaRV.omit(g2_1)
g2_2<-subset(total,select=c(NORDEMP,profoversales,Management,lnfape,lnempltot,staff_with_college_degree,CIIU4,dpto))
g2_2<-NaRV.omit(g2_2)
g2_3<-subset(total,select=c(NORDEMP,lnRDi_per_empl1,Management,lnfape,lnempltot,staff_with_college_degree,CIIU4,dpto))
g2_3<-NaRV.omit(g2_3)


#FE:yes, with ciiu4. Dependent Variable: Log (Value Added/Employees)

m13 <- plm(log_Value_Added_per_Employee ~ Management + lnfape+lnempltot+staff_with_college_degree, 
                      index = "CIIU4",
                      effect = "individual", 
                      model = "within",
                      data = g2_1)

m14 <- plm(log_Value_Added_per_Employee ~ Management + lnfape+lnempltot+staff_with_college_degree, 
                      index = "dpto",
                      effect = "individual", 
                      model = "within",
                      data = g2_1)
#FE:No
m15<-lm(log_Value_Added_per_Employee ~ Management + lnfape+lnempltot+staff_with_college_degree,data =g2_1)


#FE:yes, with ciiu4. Dependent Variable:Log(Profits/sales)
m16 <- plm(profoversales ~ Management + lnfape+lnempltot+staff_with_college_degree, 
                      index = c("CIIU4"),
                      effect = "individual", 
                      model = "within",
                      data = g2_2)

m17 <- plm(profoversales ~ Management + lnfape+lnempltot+staff_with_college_degree, 
                      index = c("dpto"),
                      effect = "individual", 
                      model = "within",
                      data = g2_2)
#FE:No
m18<-lm(profoversales ~ Management + lnfape+lnempltot+staff_with_college_degree,data =g2_2)


#FE:yes, with ciiu4. Dependent Variable:RDi
m19 <- plm(lnRDi_per_empl1~ Management + lnfape+lnempltot+staff_with_college_degree, 
                      index = c("CIIU4"),
                      effect = "individual", 
                      model = "within",
                      data = g2_3)

#FE:yes, with ciiu4. Dependent Variable:RDi
m20 <- plm(lnRDi_per_empl1~ Management + lnfape+lnempltot+staff_with_college_degree, 
                      index = c("dpto"),
                      effect = "individual", 
                      model = "within",
                      data = g2_3)

#FE:No
m21<-lm(lnRDi_per_empl1~ Management + lnfape+lnempltot+staff_with_college_degree,data =g2_3)



#code for gravity equation
#j19 <- feglm(lnRDi_per_empl1~ Management + lnfape+lnempltot+staff_with_college_degree|CIIU4+dpto,g2_3)
#summary(j19)


#stargazer(m13,m14,m15,m16,m17,m18,m19,m20,m21,
#          header = FALSE,
#          title = "Firm Management Scores and Performance",
#          covariate.labels = c("Management", "Ln(Cap/Emp)","Ln(Emp)","Degree"),
#          dep.var.labels = c("Log(VA/Emp)","(Profits/sales)","RDi/Emp"),#,
#          model.names = FALSE,
#          omit.stat = c("ser","f","adj.rsq"), #"rsq", 
#          omit="Constant",
#          digits = 2,
#          notes.align = "l",font.size = "small")


rob_se2 <- list(sqrt(diag(vcovHC(m13, type = "HC1"))),
               sqrt(diag(vcovHC(m14, type = "HC1"))),
               sqrt(diag(vcovHC(m15, type = "HC1"))),
               sqrt(diag(vcovHC(m16, type = "HC1"))),
               sqrt(diag(vcovHC(m17, type = "HC1"))),
               sqrt(diag(vcovHC(m18, type = "HC1"))),
               sqrt(diag(vcovHC(m19, type = "HC1"))),
               sqrt(diag(vcovHC(m20, type = "HC1"))),
               sqrt(diag(vcovHC(m21, type = "HC1"))))

texreg(list(m13, m14,m15,m16,m17,m18,m19,m20,m21),caption.above = TRUE, caption="Firm Management Scores and Performance",fontsize = "small",   custom.header = list("Log(VA/Emp)"=1:3,"(Profits/sales)"=4:6, "RDi/Emp"=7:9),digits =2,override.se = rob_se2, omit.coef ="Intercept",custom.coef.names=c("Management","Ln(Cap/Emp)","Ln(Employment)","Degree"), custom.model.names =c("1","2","3","4","5","6","7","8","9"),custom.note = ("\\parbox{0.95\\linewidth}{\\vspace{3pt}%stars. \\\\OLS coefficients with standard errors in parentheses. The management score is the unweighted average of the score for each of the 16 questions, where each question is first normalized to be on a 0–1 scale. The sample is all EDIT observations with at least 11 non-missing responses to management questions and a successful match to EAM, which have positive value added, positive employment, and positive imputed capital. The columns 1-3 mean the models with Industry Fixed Effects, Location Fixed Effects and no Fixed Effects, respectively.This also applies for columns 4-6 and 7-9.}")) 

```


```{r echo=FALSE,warning=FALSE,message=FALSE,results="asis"}

# Regression for Drivers of Productivity Variation (dpv)

#IV1R11C2: total personal employed
#II1R10C2:Investment on RDi
#II1R4C2:Investment on ITC

#in order to replace NA by zeroes
g3_subset<-subset(total,select=c(NORDEMP,log_Value_Added_per_Employee,Management,lnRDi_per_empl1,ICT_per_Employee,staff_with_college_degree))


g3_1<-g3_subset
g3_1$lnRDi_per_empl1[is.na(g3_subset$lnRDi_per_empl1)] <- 0
g3_1$ICT_per_Employee[is.na(g3_subset$ICT_per_Employee)] <-256.7
g3_1<-NaRV.omit(g3_1)


reg_dpvlog1<-lm(log_Value_Added_per_Employee ~ Management, data =g3_1)
reg_dpvlog2<-lm(log_Value_Added_per_Employee ~ Management+lnRDi_per_empl1, data =g3_1)
reg_dpvlog3<-lm(log_Value_Added_per_Employee ~ Management+lnRDi_per_empl1+ICT_per_Employee, data =g3_1)
reg_dpvlog4<-lm(log_Value_Added_per_Employee ~ Management+lnRDi_per_empl1+ICT_per_Employee+staff_with_college_degree, data =g3_1)

#stargazer(reg_dpvlog1,reg_dpvlog2,reg_dpvlog3,reg_dpvlog4,
#          header = FALSE,
#          title = "Drivers of Productivity Variation",
#          dep.var.labels ="Log(Value Added /employees)",
#          covariate.labels =c("Management","RDi", "Log(ITC)","Degree"),
#          omit.stat = c("ser","f","adj.rsq"),
#          omit="Constant",
#          digits = 3)


rob_se3 <- list(sqrt(diag(vcovHC(reg_dpvlog1, type = "HC1"))),
               sqrt(diag(vcovHC(reg_dpvlog2, type = "HC1"))),
               sqrt(diag(vcovHC(reg_dpvlog3, type = "HC1"))),
               sqrt(diag(vcovHC(reg_dpvlog4, type = "HC1"))))

texreg(list(reg_dpvlog1, reg_dpvlog2,reg_dpvlog3,reg_dpvlog4),caption.above = TRUE, caption="Drivers of Productivity Variation",fontsize = "normalsize", override.se = rob_se3, custom.header = list("Log(VA/Emp)"=1:4),digits =3,omit.coef ="Intercept",custom.coef.names=c("Management","RDi", "ICT/Emp","Degree"), custom.model.names =c("1","2","3","4"),custom.note = ("\\parbox{0.6\\linewidth}{\\vspace{3pt}%stars. \\\\OLS coefficients with standard errors in parentheses.Dependent variable is firm level log(Value Added/Employment). Right-hand-side variables are Management score, RDi is measured as log(1+RDi intensity), where RDi intensity is the total domestic Research, Development and innovation expenditure in 2018 divided by total domestic employment, ICT/Emp is investment per worker (spending on information and communication technology hardware and software per employee), Degree is measured by the share of employees (managers and non-managers) with a college degree.Missing values have been replaced by zero for RDi and by means for the other variables.}"))

```




```{r echo=FALSE,warning=FALSE,message=FALSE,results="asis", fig.show='hide',results='hide'}


g4<-subset(total,select=c(NORDEMP,Management,lerner))
g4<-NaRV.omit(g4)
g5<-subset(total,select=c(NORDEMP,Management,lerner,lnfape,lnempltot,staff_with_college_degree,CIIU4))
g5<-NaRV.omit(g5)

m22<-lm( Management ~ lerner,data =g4)

#FE industry 4 digits and all controls
m23 <- plm(Management ~ lerner+lnfape+lnempltot+staff_with_college_degree, 
                      index = c("CIIU4"),
                      effect = "individual", 
                      model = "within",
                      data = g5)


rob_se3 <- list(sqrt(diag(vcovHC(m22, type = "HC1"))),
               sqrt(diag(vcovHC(m23, type = "HC1"))))

texreg(list(m22, m23),caption.above = TRUE, caption="Product Market Competition and Management", fontsize = "normalsize", custom.header = list("Management"=1:2),digits =3,override.se = rob_se3,  omit.coef ="Intercept",custom.coef.names=c("Lerner Index","Ln(Cap/Emp)", "Ln(Employment","Degree"), custom.model.names =c("1","2"),custom.note = ("\\parbox{0.6\\linewidth}{\\vspace{3pt}%stars. \\\\The Lerner Index is the gross profits over sales, where gross profits equals to production value less material costs and wage costs in 2018.This table uses this Lerner index without controls:column (1), and with four-digit industry fixed effects and full controls:column (2).}"))

```


```{r echo=FALSE,warning=FALSE,message=FALSE,results="asis"}

g5<-subset(total,select=c(NORDEMP,lnvalprod, lnwages,lnfixedassets,lnintinput))
g5<-NaRV.omit(g5)

#Total Factor Productivity (tfp)
#LogY:lnvalprod
#LogL:lnwages
#LogK:lnfixedassets
#LogI:lnintinput

mtfp_reg<-lm(lnvalprod ~ lnwages+lnfixedassets+lnintinput,data =g5)
#summary(mtfp_reg)

g5$p_lnvalprod<-predict(mtfp_reg)

g5$lna<-g5$lnvalprod-g5$p_lnvalprod


g6<-merge(g5,g3_subset[ , c("NORDEMP","Management","lnRDi_per_empl1","ICT_per_Employee","staff_with_college_degree")],by="NORDEMP",all=FALSE)
g6$lnRDi_per_empl1[is.na(g6$lnRDi_per_empl1)] <- 0
g6$ICT_per_Employee[is.na(g6$ICT_per_Employee)] <-256.7


#Revenue-based Total Factor Productivity

m24<-lm(lna ~ Management,data=g6)

m25<-lm(lna ~ Management+lnRDi_per_empl1, data =g6)

m26<-lm(lna ~ Management+lnRDi_per_empl1+ICT_per_Employee, data=g6)

m27<-lm(lna ~ Management+lnRDi_per_empl1+ICT_per_Employee+staff_with_college_degree, data =g6)

rob_se5 <- list(sqrt(diag(vcovHC(m24, type = "HC1"))),
               sqrt(diag(vcovHC(m25, type = "HC1"))),
               sqrt(diag(vcovHC(m26, type = "HC1"))),
               sqrt(diag(vcovHC(m27, type = "HC1"))))


texreg(list(m24, m25,m26,m27),caption.above = TRUE, caption="Drivers of Total Factor Productivity", fontsize = "normalsize", custom.header = list("Revenue-based Total Factor Productivity - RTFP"=1:4),digits =3,omit.coef ="Intercept",custom.coef.names=c("Management","RDi", "ICT/Emp","Degree"), override.se = rob_se5, custom.model.names =c("1","2","3","4"),custom.note = ("\\parbox{0.6\\linewidth}{\\vspace{3pt}%stars. \\\\OLS coefficients with standard errors in parentheses. Dependent variable is firm level TFP built from industry firm-level. Independent variables are management score, RDi measured as log(1+RDi intensity) where RDi intensity is the total domestic RDi expenditure divided by total domestic employment, IT investment per worker, skill measured by the share of employees (managers and non-managers) with a college
degree.Missing values have been replaced by zero for RDi and by means for the other variables.}"))




```


```{r echo=FALSE,warning=FALSE,message=FALSE,results="asis"}

#source: 

#average tariffs: https://www.macmap.org/
# ciiu-product: https://www.dane.gov.co/index.php/sistema-estadistico-nacional-sen/normas-y-estandares/nomenclaturas-y-clasificaciones/tablas-correlativas

tarciiu<- read_csv("~/Google Drive/Internship_WB_Summer/Edit/Github/My_internship/Tariffs_CIIU4.csv")
#count(tarciiu,"CIIU4")

avgtarciiu<-data.frame(aggregate( avgtariff ~ CIIU4,tarciiu, mean ))

total <- merge(total,avgtarciiu,by="CIIU4",all=FALSE)

total<-total%>%
  relocate(CIIU4, .before = TIPOLO)

##China import share
impo_china_ciiu4<-read_dta("~/Google Drive/Internship_WB_Summer/Edit/Github/My_internship/impo_china_ciiu4.dta")
total <- merge(total,impo_china_ciiu4,by="CIIU4",all.x=TRUE)
#anyNA(total$avgtariff)

g7<-subset(total,select=c(NORDEMP,Management,avgtariff,lnfape,lnempltot,staff_with_college_degree,CIIU4,lerner,chshare,dpto))
g7<-NaRV.omit(g7)


m28<-miceadds::lm.cluster( Management ~ lerner+factor(dpto),data =g7,cluster="CIIU4")

m29 <- miceadds::lm.cluster(Management ~lerner+avgtariff+factor(dpto),data = g7, cluster="CIIU4")

m30<-miceadds::lm.cluster(Management ~lerner+avgtariff+I((lerner*avgtariff))+factor(dpto), cluster="CIIU4",data =g7)

m31<-miceadds::lm.cluster(Management ~lerner+avgtariff+I((lerner*avgtariff))+lnfape+lnempltot+staff_with_college_degree+factor(dpto),cluster="CIIU4",data =g7)


m31cl<-miceadds::lm.cluster(Management~lerner+avgtariff+I((lerner*avgtariff))+lnfape+lnempltot+staff_with_college_degree+factor(dpto),cluster="CIIU4",data =g7)


#Chinese imports
m28b<-miceadds::lm.cluster( Management ~ chshare,cluster="CIIU4",data =g7)
m29b <- miceadds::lm.cluster(Management ~chshare+lnfape+lnempltot+staff_with_college_degree,cluster="CIIU4",data = g7)

texreg(list(m28, m29,m30,m31),caption.above = TRUE, caption="Market Competition and Management", fontsize = "normalsize", custom.header = list("Management"=1:4),digits =3,omit.coef =c("(Intercept)|(factor)"),custom.coef.names=c("Lerner Index","Average Tariff","Inter Lerner*Tariff","Ln(Cap/Emp)", "Ln(Employment)","Degree"), custom.model.names =c("1","2","3","4"),custom.note = ("\\parbox{0.8\\linewidth}{\\vspace{3pt}%stars. \\\\Lerner Index is the gross profits over sales, where gross profits equals to production value less material costs and wage costs in 2018.The Average Tariff is the average of the tariffs according to the ciiu 4 code of the firm.For the merge between CIIU4 and Tariffs, we use tables from DANE and International Trade Centre - ITC. In the last column, it includes  a interaction between Lerner Index and Average Tariffs and full controls. All regressions have Location Fixed Effects by department in Colombia.}"))


texreg(list(m28b, m29b),caption.above = TRUE, caption="China Import Share and Management", fontsize = "normalsize", custom.header = list("Management"=1:2),digits =3,omit.coef ="Intercept",custom.coef.names=c("China Import Share","Ln(Cap/Emp)", "Ln(Employment)","Degree"), custom.model.names =c("1","2"),custom.note = ("\\parbox{0.6\\linewidth}{\\vspace{3pt}%stars. \\\\The China Import Share means imports from China / Total imports for each industry (4 digits CIIU rev4). This table uses this China Import Share without controls:column (1), and with full controls:column (2).}"))




```



```{r echo=FALSE,warning=FALSE,message=FALSE,results="asis"}


##Listing variables Trade and Management

#Logarithms
total$lnsales_x<-log(1+total$sales_x)
total$lniraw_m<-log(1+total$raw_material_m)
total$lntrade<-log(1+total$sales_x+total$raw_material_m)

#count(total,"shareraw_m")
#anyNA(total$shareraw_m)

##Shares 
total$sharesales_x<-total$sales_x/total$sales
total$shareraw_m<-total$raw_material_m/total$raw_material
total$sharetrade<-(total$sales_x+total$raw_material_m)/(total$sales+total$raw_material)

#Dummies
#xer: Exporter
#mer: Importer
#traded: Exporter or Importer
total<-total %>%
  mutate(xer = if_else(sales_x >0, 1,0))%>%
  mutate(mer = if_else(raw_material_m >0, 1,0))%>%
  mutate(traded=if_else(sales_x+raw_material_m>0,1,0))

sum(total$xer)

# Logarithm and dummies REGRESSIONS
g8<-subset(total,select=c(NORDEMP,xer,mer,traded,lnsales_x,lniraw_m,lntrade,Management,dpto,lnfape,lnempltot,staff_with_college_degree,CIIU4))
g8<-NaRV.omit(g8)

#Logarithms
m32<-miceadds::lm.cluster(lnsales_x ~Management+lnfape+lnempltot+staff_with_college_degree+factor(CIIU4)+factor(dpto),data = g8,cluster = "CIIU4")
m33<-miceadds::lm.cluster(lniraw_m ~Management+lnfape+lnempltot+staff_with_college_degree+factor(CIIU4)+factor(dpto),cluster = "CIIU4",data = g8)
m34<-miceadds::lm.cluster(lntrade ~Management+lnfape+lnempltot+staff_with_college_degree+factor(CIIU4)+factor(dpto),cluster = "CIIU4",data = g8)

#Dummies
m35<-miceadds::lm.cluster(xer ~Management+lnfape+lnempltot+staff_with_college_degree+factor(CIIU4)+factor(dpto),cluster = "CIIU4",data = g8)
m36<-miceadds::lm.cluster(mer ~Management+lnfape+lnempltot+staff_with_college_degree+factor(CIIU4)+factor(dpto),cluster = "CIIU4",data = g8)
m37<-miceadds::lm.cluster(traded ~Management+lnfape+lnempltot+staff_with_college_degree+factor(CIIU4)+factor(dpto),cluster = "CIIU4",data = g8)

#Share REGRESSION
g9<-subset(total,select=c(NORDEMP,sharesales_x,shareraw_m,sharetrade,Management,dpto,lnfape,lnempltot,staff_with_college_degree,CIIU4))
g9<-NaRV.omit(g9)

m38<-miceadds::lm.cluster(sharesales_x ~Management+lnfape+lnempltot+staff_with_college_degree+factor(CIIU4)+factor(dpto),cluster = "CIIU4",data = g9)
m39<-miceadds::lm.cluster(shareraw_m ~Management+lnfape+lnempltot+staff_with_college_degree+factor(CIIU4)+factor(dpto),cluster = "CIIU4",data = g9)
m40<-miceadds::lm.cluster(sharetrade ~Management+lnfape+lnempltot+staff_with_college_degree+factor(CIIU4)+factor(dpto),cluster = "CIIU4",data = g9)


texreg(list(m32, m33,m34),caption.above = TRUE, caption="Logarithms of trade outcomes and Management", fontsize = "normalsize",digits =3,custom.coef.names=c("Management","Ln(Cap/Emp)","Ln(Employment)","Degree"), custom.model.names =c("Log(1+Exports)","Log(1+Imports)","Log(1+Exports+Imports)"),omit.coef =c("(Intercept)|(factor)"),custom.note = ("\\parbox{0.8\\linewidth}{\\vspace{3pt}%stars. \\\\This table examines the relationship between logartithm of (1+value of exported products), logarithm of (1+value of imported inputs) and logarithm of (1+value of exported products + imported inputs) at firm level and firm's management practices.It includes some controls: Ln(Cap/Emp), Ln(Employment) and the percent of staff with college degree. All regressions include fixed effects for firm location (department) and 4 digits - CIIU 4 (industry).}"))


texreg(list(m35,m36,m37),caption.above = TRUE, caption="Dummies of trade outcomes and Management", fontsize = "normalsize",digits =3,custom.coef.names=c("Management","Ln(Cap/Emp)","Ln(Employment)","Degree"), custom.model.names =c("Dummy Exports","Dummy Imports","Dummy Trade"),omit.coef =c("(Intercept)|(factor)"),custom.note = ("\\parbox{0.8\\linewidth}{\\vspace{3pt}%stars. \\\\This table examines the relationship between export status (Dummy Exports = 1 if value of exported products>0 and 0 otherwise), import status (Dummy Import=1 if value of imported inputs>0 and 0 otherwise), trade status (Dummy Trade=1 if value of exports + imports>0 and 0 otherwise) and firm's management practices.It includes some controls: Ln(Cap/Emp), Ln(Employment) and the percent of staff with college degree. All regressions include fixed effects for firm location (department) and 4 digits - CIIU 4 (industry).}"))

texreg(list(m38,m39,m40),caption.above = TRUE, caption="Shares of trade outcomes and Management", fontsize = "normalsize",digits =3,custom.coef.names=c("Management","Ln(Cap/Emp)","Ln(Employment)","Degree"), custom.model.names =c("Share of exported products","Share of imported inputs","Share of traded"),omit.coef =c("(Intercept)|(factor)"),custom.note = ("\\parbox{0.9\\linewidth}{\\vspace{3pt}%stars. \\\\This table examines the relationship between Share of exported products = exports/total sales, Share of imported inputs=imports/total inputs, Share of traded=(exports+imports)/(total sales + inputs) and firm's management practices.It includes some controls: Ln(Cap/Emp), Ln(Employment) and the percent of staff with college degree. All regressions include fixed effects for firm location (department) and 4 digits - CIIU 4 (industry).}"))


```

```{r echo=FALSE,warning=FALSE,message=FALSE,results="asis"}

# Homogeneous and Heterogeneous
rauch<- read_csv("~/Google Drive/Internship_WB_Summer/Edit/Github/My_internship/Sitc_con_lib_ciiu4July23_.csv")

rauch_unique<-rauch[!duplicated(rauch$CIIU4), ]

total<-merge(total,rauch_unique,by="CIIU4",all.x = TRUE)
#count(total,"LIBERAL")

total<-total%>%
  mutate(dummy_diff=ifelse(LIBERAL=="n",1,0))

g10<-subset(total,select=c(NORDEMP,xer,mer,traded,lnsales_x,lniraw_m,lntrade,Management,dummy_diff,dpto,lnfape,lnempltot,staff_with_college_degree,CIIU4))
g10<-NaRV.omit(g10)

m41<-miceadds::lm.cluster(lnsales_x ~Management+I((Management*dummy_diff))+lnfape+lnempltot+staff_with_college_degree+factor(dpto),cluster="CIIU4",data = g10)


texreg(list(m41),caption.above = TRUE, caption="Differentiated Products and Management", fontsize = "normalsize",digits =3,custom.coef.names=c("Management","Inter Manag*Diff", "Ln(Cap/Emp)","Ln(Employment)","Degree"), custom.model.names =c("Log(1+Exports)"),omit.coef =c("(Intercept)|(factor)"),custom.note = ("\\parbox{0.6\\linewidth}{\\vspace{3pt}%stars. \\\\This table examines the relationship between logartithm of (1+value of exported products) at firm level and firm's management practices.It includes  a interaction between Management and a Dummy of Differentiated Product:Inter Manag*Diff= 1 when the firm product is differentiated and O otherwise, using Rauch clasiffication. Since Rauch(1999) classifies products at the level of 4 digits of industry, this table assumes that the firm produces only one good, either homogeneous or differentiated, according to its industry(CIIU rev4).In addition, it includes full controls: Ln(Cap/Emp), Ln(Employment) and the percent of staff with college degree. The regression has fixed effects for firm location (department).}"))


```



```{r echo=FALSE,warning=(FALSE),message=FALSE}

set1<-subset(total,select=c(NORDEMP,Management,lnempltot,empltot,CIIU4,RDi,lnRDi_per_empl1,ipr))
write_dta(set1,"~/Google Drive/Internship_WB_Summer/Edit/Github/Data_Pulso/set1.dta")

write_dta(total,"~/Google Drive/Internship_WB_Summer/Edit/Github/My_internship/total.dta")

#fig.width = 2.5, fig.height=2.5

#graphs (three first questions)

# 1. Property

q1<-ggplot(Edit_2017_2018_2) +
  geom_bar(aes(x =property,group=1)) +
  labs(title = "Graph1.Who is the largest shareholder?",
       y="Frequency")+theme(plot.title = element_text(size = 8, face = "bold"))+theme(plot.title = element_text(hjust = 0.3))

#q1

# 2. Manager and property

Edit_2017_2018_2<-Edit_2017_2018_2%>%
  mutate(manager=ifelse(VIII2R1C1==1,"Yes","No"))

q2<-ggplot(Edit_2017_2018_2) +
  geom_bar(aes(x =factor(manager),y=..prop..,group=1)) +
  labs(title = "Is the manager the same founder or founder's family member?",
       y="Proportion",x="Manager")+theme(plot.title = element_text(size = 6, face = "bold"))+theme(plot.title = element_text(hjust = 0.3))

#q2

# 3. Gender

Edit_2017_2018_2<-Edit_2017_2018_2%>%
  mutate(gender=ifelse(VIII3R1C1==1,"Man","Woman"))

q3<-ggplot(Edit_2017_2018_2) +
  geom_bar(aes(x =factor(gender),y=..prop..,group=1)) +
  labs(title = "Manager Gender",
       x="Gender",
       y="Proportion")+theme(plot.title = element_text(hjust = 0.5))+theme(plot.title = element_text(size = 8, face = "bold"))

#q3

ggarrange(q1, q2, q3 +rremove("x.text"),
        ncol = 2, nrow = 2,widths = 0.5,heights = 0.5)+theme(plot.title = element_text(hjust = 0.5))

NORDEMP=subset(total, select = c(NORDEMP))
#write_dta(NORDEMP,"~/Google Drive/Internship_WB_Summer/Edit/Github/My_internship/NORDEMP.dta")


count(total,"ciiu4_2_d")

#weighted input tariffs
wit<- read_csv("~/Google Drive/Internship_WB_Summer/Edit/Github/My_internship/weighted_input_tariffs.csv")

total<-merge(total,wit,by="ciiu4_2_d",all.x=TRUE)

total<-total%>%
  relocate(ciiu4_2_d, .before = wit)%>%
  relocate(CIIU4, .before = ciiu4_2_d)

```

```{r echo=FALSE,warning=FALSE,message=FALSE,results="asis"}

total<-merge(total,g5[ , c("NORDEMP","lna")],by="NORDEMP",all.x =TRUE)

total$avgtariff_2 <- ave(total$avgtariff, total$ciiu4_2_d)

total<-total%>%
  relocate(avgtariff, .before = wit)

m42<-lm(Management ~ avgtariff_2+wit,data=total)
summary(m42)

total$logwit<-log(total$wit+1)

total$logavgtariff<-log(total$avgtariff+1)

count(total,"logwit")






```

